The \dealii{} Library, Version 9.3

### 2021-06-20 9.3/paper.tex
Update 9.3/paper.tex
Co-authored-by: Martin Kronbichler <kronbichler@lnm.mw.tum.de>

The major changes of this release are:
%
\begin{itemize}
  \item Experimental support for simplex and mixed meshes (see Section~\ref{subsec:simplex});
  \item Improved flexibility of the particle infrastructure (see Section~\ref{subsec:particles});
  \item Support for global-coarsening multigrid algorithms (see Section~\ref{subsec:mg});
  \item Advances in the matrix-free infrastructure  (see Section~\ref{subsec:mf});
  \item Usage of MPI-3.0 shared-memory features to reduce memory footprint  (see Section~\ref{subsec:sm});
  \item Improved support for evaluation and integration at arbitrary points (see Section~\ref{subsec:fepointvalues});
  \item Simplified implementation for cell face integrals (see Section~\ref{subsec:feinterfacevalues});
  \item Nine new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%
In addition, we discuss the \candi{} installation program in Section~\ref{subsec:candi}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simplied implementation for cell face integrals}
\label{subsec:feinterfacevalues}
Discontinuous Galerkin (DG) methods require evaluations of averages and jumps accross cell faces, therefore we need to compute values of the shape functions and solutions from two adjacent cells. The \texttt{FEInterfaceValues} class is designed to provide an interface to directly obtain jumps and averages. When used with \texttt{MeshWorker::mesh\_loop()}, we can assemble cell face integrals in a uniform way independent of mesh types, which significantly simplifies the implementation.

@@

Examples of \texttt{FEInterfaceValues} for scalar problems can be found in \texttt{step-12}, \texttt{step-47}, \texttt{step-50}, and the new tutorial \texttt{step-74}. While examples of vector-valued problems will be added in the future.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
in combination with \texttt{MeshWorker::mesh\_loop()}. This tutorial demonstrates a
simple and mesh-independent way to assemble cell face integrals.

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Experimental support for simplex and mixed meshes (see Section~\ref{subsec:simplex});
  \item Improved flexibility of the particle infrastructure (see Section~\ref{subsec:particles});
  \item Support for global-coarsening multigrid algorithms (see Section~\ref{subsec:mg});
  \item Advances in the matrix-free infrastructure  (see Section~\ref{subsec:mf});
  \item Usage of MPI-3.0 shared-memory features to reduce memory footprint  (see Section~\ref{subsec:sm});
  \item Improved support for evaluation and integration at arbitrary points (see Section~\ref{subsec:fepointvalues});
  \item Simplified implementation for face integrals (see Section~\ref{subsec:feinterfacevalues});
  \item Nine new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%
In addition, we discuss the \candi{} installation program in Section~\ref{subsec:candi}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simplied implementation for face integrals}
\label{subsec:feinterfacevalues}
Discontinuous Galerkin (DG) methods require evaluations of averages and jumps accross cell faces, therefore we need to compute values of the shape functions and solutions from two adjacent cells. The \texttt{FEInterfaceValues} class is designed to provide an interface to directly obtain jumps and averages. When used with \texttt{MeshWorker::mesh\_loop()}, we can assemble face integrals in a uniform way independent of mesh types, which significantly simplifies the implementation.

@@

Examples of \texttt{FEInterfaceValues} for scalar problems can be found in \texttt{step-12}, \texttt{step-47}, \texttt{step-50}, and the new tutorial \texttt{step-74}. Examples of vector-valued problems will be added in the future.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
in combination with \texttt{MeshWorker::mesh\_loop()}. This tutorial demonstrates a
simple and mesh-independent way to assemble face integrals.
